sem

### 2023-02-14 scripts/workshop/sem.Rmd
latent model w/ lagged data

```{r}
potential_formula_1 <- "
potential =~ log_cc + log_size + inv_temp 
Prevalence ~ potential
"

@@

>>>>

```{r}
potential_formula_1 <- "\n potential =~ log_cc + log_size + inv_temp \n Prevalence ~ potential"

@@

Again with lagged data

```{r}
lag_potential <- clean %>% ungroup() %>% mutate(log_cc = log10(lag_cc), log_size = log10(lag_size), inv_temp = lag_temp*-1) %>% select(log_cc, log_size, inv_temp, Prevalence) %>% drop_na() %>% filter(inv_temp < 0)
indicators <- lag_potential %>% select(log_cc, log_size, inv_temp)
cor(indicators)

```{r}
potential_formula_2 <- "\n potential =~ log_cc + log_size + inv_temp \n Prevalence ~ potential"

potential_model_2 <- sem(potential_formula_1, lag_potential)
```

```{r}
summary(potential_model_2)
```
